$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-08 paper/paper.tex
On Orchard's work

Allais \cite{Allais2018a} uses leftover typing to mechanise in Agda a bidirectional type system for the linear \lambdacalc{}.
He proves type preservation and provides a decision procedure for type checking and type inference.
In our paper, we apply leftover typing to the \picalc{} following Allais \cite{Allais2018a}, and focus on type checking. We give a more general usage algebra, leading to linear, graded and shared type systems.
Drawing from quantitative type theory (by McBride and Atkey \cite{McBride2016, Atkey2018}), in our work, we too are able to talk about fully consumed resources.
As such, we can transmit over a channel the $\lz$ multiplicities of a fully exhausted channel.
%
Orchard et al. introduce Granule \cite{Orchard}, a fully-fledged functional language with graded modal types, linear types, indexed types and polymorphism.
Modalities include exact usages, security levels and intervals.
%Grade terms allow for grade polymorphism and their resource algebra is based on a pre-ordered semiring where addition is partial.
%They provide bidirectional typing rules, and show the type safety of their semantics.
Their types resemble our graded types, but we focus on concurrency and one of our goals is mechanisation in Agda.

>>>>

Allais \cite{Allais2018a} uses leftover typing to mechanise in Agda a bidirectional type system for the linear \lambdacalc{}.
He proves type preservation and provides a decision procedure for type checking and type inference.
In our paper, we apply leftover typing to the \picalc{} following Allais \cite{Allais2018a}, and focus on type checking. We give a more general usage algebra, leading to linear, graded and shared type systems.
Drawing from quantitative type theory (by McBride and Atkey \cite{McBride2016, Atkey2018}), in our work, we too are able to talk about fully consumed resources.
As such, we can transmit over a channel the $\lz$ multiplicities of a fully exhausted channel.
%
Orchard et al. introduce Granule \cite{Orchard}, a fully-fledged functional language with graded modal types, linear types, indexed types and polymorphism.
Modalities include exact usages, security levels and intervals; resource algebras are pre-ordered semirings with partial addition.
They provide bidirectional typing rules, and show the type safety of their semantics.
